Technology-based aids for people affected by Autism Spectrum Disorder (ASD)

### 2017-11-21 paper.tex
Checked introduction

% TODO Brief presentation of ASD (?)
\gls{asd} is a term used to cover a very big set of disorders. There are a lot of studies and experiments in this field, but still a lot questions about it are unresolved \DP{forse unknown non è il massimo come termine qui} \cri{Prova a vedere se così ti piace}: for example, the symptoms are well known, while the causes are still mostly unknown. Nowadays \textit{screening tests} are used to classify a person as affected by \gls{asd}, but these tests have an high percentage of error (false positive or negative) and they can be administered to a patient who is at least 3 years old. For this reason, several techniques have been studied in order to establish if a children has this disorder in the first 2 years of life.

>>>>

% TODO Brief presentation of ASD (?)
\gls{asd} is a term used to cover a very big set of disorders. There are a lot of studies and experiments in this field, but still a lot questions about it are unresolved: for example, the symptoms are well known, while the causes are still mostly unknown. Nowadays \textit{screening tests} are used to classify a person as affected by \gls{asd}, but these tests have an high percentage of error (false positive or negative) and they can be administered to a patient who is at least 3 years old. For this reason, several techniques have been studied in order to establish if a children has this disorder in the first 2 years of life.
